Postural changes mediate children's visual access to social information

### 2018-01-16 writeup-cogsci-jan14/cogsci2018_faceOnly.Rmd
resolve conflicts

\begin{table}[ht]
\centering
\begin{tabular}{rllrrr}
  \hline
 & detectorType & sample\_type & p & r & f \\ 
  \hline
1 & MTCNN & high\_density & 0.841 & 1.000 & 0.914 \\ 
  2 & MTCNN & random & 0.947 & 0.750 & 0.837 \\ 
  3 & OpenPose & high\_density & 0.995 & 0.863 & 0.924 \\ 
  4 & OpenPose & random & 0.710 & 0.917 & 0.800 \\ 
  5 & ViolaJones & high\_density & 0.991 & 0.495 & 0.660 \\ 
  6 & ViolaJones & random & 0.389 & 0.292 & 0.333 \\ 
   \hline
\end{tabular}
\caption{Detector performance} 
\end{table}

@@

```
```{r detByNaming, fig.env="figure", fig.pos = "H", fig.align = "center", fig.width=3, fig.height=3, fig.cap = "Proportion face detections as a function of infants's posture"  }
ggplot(aroundNamings, aes(x = factor(posture), y = face, color=posture)) + 
  geom_boxplot() + 
  ylab("Proportion of face detections within naming window") + 
  xlab("Posture") + 
  theme_bw() 
```
## Access to Faces During Labeling Events
Finally, we analyzed how face detections changed during object labeling events as a function of infant's posture and orientation.  Specfically, we analyzed a four-second window around each labeling event (e.g., "Look at the [zem]!"); these labeling events were hand-annotated and automatically synchronized with the frame-by-frame face detections. We again found that infant's posture impacted the degree to which they saw their caregiver's face during a labeling event; infants who were sitting or standing were more likely to have access to their caregiver's face.

>>>>

\begin{table}[ht]
\centering
\begin{tabular}{rllrrr}
  \hline
 & detectorType & sample\_type & p & r & f \\ 
 & Algorithm & Sample\ Type & P & R & F \\ 
  \hline
1 & MTCNN & high\_density & 0.841 & 1.000 & 0.914 \\ 
  2 & MTCNN & random & 0.947 & 0.750 & 0.837 \\ 
  3 & OpenPose & high\_density & 0.995 & 0.863 & 0.924 \\ 
  4 & OpenPose & random & 0.710 & 0.917 & 0.800 \\ 
  5 & ViolaJones & high\_density & 0.991 & 0.495 & 0.660 \\ 
  6 & ViolaJones & random & 0.389 & 0.292 & 0.333 \\ 
   \hline
\end{tabular}
\caption{Detector performance} 
\end{table}

@@

ggplot(aroundNamings, aes(x = factor(posture), y = face, color=posture)) + 
  geom_boxplot() + 
  ylab("Proportion of face detections within naming window") + 
  ylab("Prop. face detections in naming window") + 
  xlab("Posture") + 
  theme_bw() 
```
## Access to Faces During Labeling Events
Finally, we analyzed how face detections changed during object labeling events as a function of infant's posture and orientation.  Specfically, we analyzed a four-second window around each labeling event (e.g., "Look at the [zem]!"); these labeling events were hand-annotated and automatically synchronized with the frame-by-frame face detections. We again found that infant's posture impacted the degree to which they saw their caregiver's face during a labeling event; infants who were sitting or standing were more likely to have access to their caregiver's face.
